Capstone Movielens Report

### 2025-11-05 reports/capstone-movielens.site/05.appendix.Rmd
Appendix B: Models Training Datasets: move to a new page.
Appendix B, "`edx.sgr` Object" section updated.

We use the array representation described in [Section 18.5 *Analysis of variance (ANOVA)*](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova) of the _Course Textbook (New Edition)_, for the training data[@IDS2_18-5]. For this purpose, we will convert the `edx` dataset into a matrix using the `tidyr::pivot_wider` function:

@@

To account for the Movie Genre Effect more accurately, we need a dataset with split rows for movies belonging to multiple genres:
```{r eval=FALSE}
  put_log("Function: `make_source_datasets`: 
To account for the Movie Genre Effect, we need a dataset with split rows 
for movies belonging to multiple genres.")
  edx.sgr <- splitGenreRows(edx)
```
```{r}
str(edx.sgr)
summary(edx.sgr)
```

Note that we use the [splitGenreRows](#func.splitGenreRows) function described above to split rows of the original dataset:
```{r eval=FALSE}
splitGenreRows <- function(data){
  put("Splitting dataset rows related to multiple genres...")
  start <- put_start_date()
  gs_splitted <- data |>
    separate_rows(genres, sep = "\\|")
  put("Dataset rows related to multiple genres have been splitted to have single genre per row.")
  put_end_date(start)
  gs_splitted
}
```

::: {.noteblock data-latex=""}
The [source code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L73) of the function mentioned above is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
:::

>>>>

We use the array representation described in [Section 18.5 *Analysis of variance (ANOVA)*](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova) of the _Course Textbook (New Edition)_, for the training data[@IDS2_18-5]. For this purpose, we will convert the `edx` dataset into a matrix using the [tidyr::pivot_wider](https://www.rdocumentation.org/packages/tidyr/versions/1.3.0/topics/pivot_wider) function:

@@

To account for the Movie Genre Effect more accurately, we need a dataset with split rows for movies belonging to multiple genres:
```{r eval=FALSE}
  put_log("Function: `make_source_datasets`: 
To account for the Movie Genre Effect, we need a dataset with split rows 
for movies belonging to multiple genres.")
  edx.sgr <- splitGenreRows(edx)
```

::: {.noteblock data-latex=""}
We use the [splitGenreRows](#func.splitGenreRows) function (described in the [Data Processing Functions] section of the [Appendix A: Support Function]) to split rows of the original dataset.
:::

```{r}
str(edx.sgr)
summary(edx.sgr)
```
